D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Future Directions: Add material from Section 7.4
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This paper considers only fragments of programs whose threads
communicate using shared memory.
Future work might include the effects of input and output, as well
as code that reads out the current time, that uses thread IDs,
or that operates on pointer values.

Finally, future work might more precisely delineate the limits of
quasi-volatile behavior.

>>>>

This paper shows that semantic dependencies are relative to specific
executions of a program rather than strictly of the source code of that
program.
Future work might expand on
Section~\ref{sec:Relative versus Absolute Dependency},
further exploring absolute semantic dependencies that are special cases
where semantic dependencies can be a function strictly of the source code.

This paper considers only fragments of programs whose threads
communicate using shared memory.
Future work might include the effects of input and output, as well as
code that reads out the current time, that uses thread IDs, or that
operates on pointer values
(see Section~\ref{sec:Effect of Memory Layout}).

Finally, future work might expand on
Sections~\ref{sec:Global Analysis and Volatile versus Quasi Volatile},
and~\ref{sec:Merging Quasi-Volatile Loads}
so as to more precisely delineate the limits of permissible quasi-volatile
behavior.
